\begin{titlepage}
	\thispagestyle{empty}
	\parindent 0pt
	\vfill
	%\large

	\begin{center}
	\LARGE{\bf \textsf{CS246: Mining Massive Datasets} \\*[4ex]
	\Large{
	Assignment number: $3$\hrulefill \\
	Submission time: \hrulefill \quad and date: \hrulefill } }
	\end{center}

	\vfill

	Fill in and include this cover sheet with each of your assignments. It is an honor code violation to write down the wrong time. Assignments are due at 9:30 am, either handed in at the beginning of class or left in the submission box on the $1^{st}$ floor of the Gates building, near the east entrance. Failure to include the coversheet with you assignment will be penalized by 2 points.

	Each student will have a total of {\em two} free late periods. {\em One late period expires at the start of each class.} (Assignments are due on Thursdays, which means the first late period expires on the following Tuesday at 9:30am.) Once these late periods are exhausted, any assignments turned in late will be penalized 50\% per late period. However, no assignment will be accepted more than {\em one} late period after its due date. (If an assignment is due to Thursday then we will not accept it after the following Thursday.) 

	\vfill
	\bigskip
	\vfill

	{\Large
	\textbf{Your name:} Bla\v{z} Sovdat\hrulefill \\
	\textbf{Email:} blaz.sovdat@gmail.com\underline{\hspace*{7cm}} \textbf{SUNet ID:} \hrulefill\\*[2ex] }
	Collaborators:\hrulefill
	\vfill

	I acknowledge and accept the Honor Code.\\*[3ex]
	\bigskip
	\textit{(Signed)}\hrulefill

	\vfill
	\vfill

	\begin{center}
	\normalsize{(For CS246 staff only)\\
	\bigskip
	Late days:\quad 0 \quad 1 }
	\end{center}


	\begin{center}
	\linespread{1.3}
	\large
	\begin{tabular}{|c|r|}\hline
	Section & \hspace*{1.5cm} Score \\ \hline \hline
	1 &  \\ \hline
	2 &  \\ \hline
	3 &  \\ \hline
	4 &  \\ \hline
	\hline
	Total & \hspace*{1cm} \\ \hline
	\end{tabular}
	\end{center}
	Comments: /
\end{titlepage}
